On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-06-07 Manuscript/manuscript.tex
Small Manuscript Update

\paragraph{Student's $t$ CI}
The procedure for constructing a Student's $t$ CI based on standard bootstrap is
described in \citet{efron1993introduction}. \jy{give page or section number when
  citing a book}
With block bootstrapping, a $(1 - \alpha)100\%$ Student's $t$ CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\hat{\text{SE}}, \quad
\hat{\theta}_{n} - t_{(\alpha/2), k -1}\hat{\text{SE}}),
\]
\eds{define $t_{(.)}$ and check the signs}
where $k$ is the number of blocks.
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
Like the standard 
normal interval, the Student's $t$ CI is a table-based bootstrap interval
approach. In this case,
its validity relies on whether the distribution of $\hat\theta_n$ is
reasonably well approximation by the $t_{k-1}$ distribution with an
expected value of $\theta$, and whether the bootstrap 
$\widehat{\text{SE}}$ approximates the true standard error.

@@

\paragraph{Proposed Method CI}
Our Proposed Method CI is centered at the point estimator and uses the
variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$.
A $(1 - \alpha)100\%$ CI using our Proposed Method is
\[
(\hat\theta_{n, \alpha/2}^{(b)} - \widehat{\text{bias}}, \quad
\hat\theta_{n, 1 - \alpha/2}^{(b)} - \widehat{\text{bias}}).
\]
This CI is necessarily centered around .... and
is asymmetric, as different critical values are used to compute
the lower and upper bounds.

@@

This study could be used as a guide for applied statistics courses for students
to generally understand how large of a sample size is sufficient for block
bootstrap to be used versus other inference methods.
This information could also prove to be useful for research using block
bootstrap
estimation of time series in domains such as econometrics. Future studies
could investigate if there are types of block bootstrap interval
construction such as $ABC$ or bootstrap-t intervals
that would more appropriately recover the parameters of a time
series. \eds{are there other methods that you know of?} 
One could also investigate the $n$ needed to make inferences about
other forms of serially dependent data such as a moving average process.

>>>>

\paragraph{Student's $t$ CI}
The procedure for constructing a Student's $t$ CI based on standard bootstrap is
described in \citet[p.158]{efron1993introduction}. \jy{give page or section number when
  citing a book} \mc{addressed}
With block bootstrapping, a $(1 - \alpha)100\%$ Student's $t$ CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\hat{\text{SE}}, \quad
\hat{\theta}_{n} - t_{(\alpha/2), k -1}\hat{\text{SE}}),
\]
\eds{define $t_{(.)}$ and check the signs}
where $k$ is the number of blocks.
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
Like the standard 
normal interval, the Student's $t$ CI is a table-based bootstrap interval
approach. In this case,
its validity relies on whether the distribution of $\hat\theta_n$ is
reasonably well approximation by the $t_{k-1}$ distribution with an
expected value of $\theta$, and whether the bootstrap 
$\widehat{\text{SE}}$ approximates the true standard error.

@@

\paragraph{Proposed Method CI}
Our Proposed Method CI is centered at the point estimator and uses the
variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$.
A $(1 - \alpha)100\%$ CI using our Proposed Method is
\[
(\hat\theta_{n, \alpha/2}^{(b)} - \widehat{\text{bias}}, \quad
\hat\theta_{n, 1 - \alpha/2}^{(b)} - \widehat{\text{bias}}).
\]
This CI is necessarily centered around $\hat\theta_n$ and can also be rewritten
as 
\[
(\hat\theta_n + \hat\theta_{n, \alpha/2}^{(b)} - \bar\theta_n^{(b)}, \quad
\hat\theta_n + \hat\theta_{n, 1 - \alpha/2}^{(b)} - \bar\theta_n^{(b)}).
\]
and is asymmetric, as different critical values are used to compute
the lower and upper bounds.

@@

This study could be used as a guide for applied statistics courses for students
to generally understand how large of a sample size is sufficient for block
bootstrap to be used versus other inference methods. For undergraduate or
graduate students, block bootstrap is not typically a part of curriculum, but the 
results of this study can easily be used to demonstrate when it is practical to use 
this method.
This information could also prove to be useful for research using block
bootstrap
estimation of time series in domains such as econometrics. Future studies
could investigate if there are types of block bootstrap interval
construction such as $ABC$ or bootstrap-t intervals
that would more appropriately recover the parameters of a time
series. \eds{are there other methods that you know of?} 
One could also investigate the $n$ needed to make inferences about
other forms of serially dependent data such as a moving average process.
